%% start of file `Jean-Pierre.Chauvel.Résumé.full.tex`
%% Copyright 2016 Jean-Pierre Chauvel <jean.pierre@chauvel.org>

\documentclass[11pt,a4paper,english]{moderncv}
% moderncv theme
\moderncvtheme[grey]{casual}
% document language
\usepackage[english]{babel}
% character encoding
\usepackage[utf8]{inputenc}
% adjust page margins
\usepackage[scale=0.8]{geometry}
% in preamble:
\SetExpansion[stretch = 70, shrink = 70,] { encoding = {T2A} } { }
\DeclareMicrotypeSet{t2atext}{encoding=T2A}
\UseMicrotypeSet{t2atext}

%personal data
\name{Jean-Pierre}{Chauvel}
\address{Lima, Perú}{}
%\email{jean.pierre@chauvel.org}
\email{jean.pierre@chauvel.org}
\homepage{www.chauvel.org}
%\social[twitter]{hellhoundorf}
\social[whatsapp]{+51989804478}
\social[linkedin]{jpchauvel}
\social[github]{jpchauvel}
\quote{Boasting nearly two decades of crafting enterprise solutions, I stand as a champion of agile methodologies with a robust Python backend expertise. My affinity for Vim epitomizes my fusion of classic rigor with contemporary agility.}

\begin{document}
\maketitle

\section{Recent Experience}

\cventry{2017--Present}{Senior Python Software Engineer}{Encora}{Lima--Peru}{}
{
\url{https://encora.com}
\newline{}
\begin{itemize}
    \item \textbf{Goodyear's AndGo}
        \newline{}
        \url{https://www.andgonow.com}
        \begin{itemize}
            \item Spearheaded the creation of comprehensive technical specifications and diagrams to crystallize product requirements, facilitating seamless communication between developers and stakeholders.
            \item Implemented Test-Driven Development (TDD) diligently, maintaining code coverage above 90\% for unit, integration, and end-to-end tests, ensuring robust and reliable software deliveries.
            \item Played a pivotal role in decomposing a monolithic service into a suite of focused microservices, taking utmost care in rearchitecting database schema for scalability and resilience.
            \item Led the development of a critical feature for the automation of calendar events, enhancing process efficiency through meticulous forward-planning.
        \end{itemize}
        \textbf{Tools:} Python, asyncio, Flask, SQLAlchemy, PostgreSQL, Mock, Git, Docker, Microservices
    \item \textbf{Tribal Planet's MPACT}
        \newline{}
        \url{https://www.tribalplanet.com}
        \begin{itemize}
            \item Orchestrated the architectural blueprint and championed backend development, maintaining cutting-edge application infrastructure.
            \item Elevated test coverage with a TDD approach for a watertight, bug-resistant production environment.
            \item Innovated a robust continuous deployment pipeline using CircleCI and AWS EKS to streamline software delivery. 
            \item Augmented performance by offloading computationally intensive tasks to Celery jobs, optimizing asynchronous operations.
            \item Engineered an automated content moderation system using AWS Rekognition and Azure Cognitive Services that upheld content quality and compliance.
        \end{itemize}
        \textbf{Tools:} Python, asyncio, Flask, SQLAlchemy, MySQL, MongoDB, Mock, Git, Docker
    \item \textbf{Scotiabank's mobile banking}
        \begin{itemize}
            \item Contributed to the development of the iOS app using Objective-C, ensuring adherence to industry best practices and a consistent user experience.
            \item Upheld TDD principles to guarantee comprehensive unit test coverage, fostering reliability in app releases.
            \item Utilized the GitFlow branching model to maintain a stable and methodical software versioning rhythm.
        \end{itemize}
        \textbf{Tools:} Objective-C, Swift 4.1, Carthage, Git
\end{itemize}
}

\subsection{}

\cventry{2017}{iOS Software Engineer}{Dipoo SAC}{Lima--Perú}{}
{
\begin{itemize}
    \item \textbf{Bederr}
        \begin{itemize}
            \item Actively engaged in the enhancement and expansion of the iOS application by employing Objective-C, meticulously ensuring that each module aligns with the prevailing industry standards and best practices, thereby delivering a seamless and uniform user experience across various device platforms.
            \item Diligently adhered to Test-Driven Development (TDD) methodologies to ensure the implementation of robust unit testing, which significantly contributes to the stability and reliability of the application, thereby minimizing disruptions in production and enhancing user satisfaction with each software release.
            \item Implemented the GitFlow branching strategy to systematically manage the development and release processes, ensuring a disciplined and consistent approach to software versioning, which facilitates smoother transitions and updates in the application lifecycle, enhancing team collaboration and efficiency in handling project timelines.
        \end{itemize}
        \textbf{Tools:} Objective-C (iOS), OCMockito, Core Location, Google Maps, Circle CI, Hock- eyApp, CocoaPods
\end{itemize}
}

\subsection{}

\cventry{2016-2017}{iOS Software Engineer}{Freelance}{Lima--Perú}{}
{
\begin{itemize}
    \item \textbf{Aldo Mariátegui’s Ensayos Impopulares}
        \begin{itemize}
            \item Contributed to the development of the iOS app using Objective-C, ensuring adherence to industry best practices and a consistent user experience.
            \item Upheld TDD principles to guarantee comprehensive unit test coverage, fostering reliability in app releases.
            \item Utilized the GitFlow branching model to maintain a stable and methodical software versioning rhythm.
        \end{itemize}
        \textbf{Tools:} Objective-C (iOS), AFNetworking, OCUnit (SenTestingKit), OCHamcrest, Python, Django, Django RESTFramework, nose, Mock, Gunicorn, Supervisord, XML, Travis-CI, Fabric
\end{itemize}
}

\subsection{}

\cventry{2016}{Senior Python Software Engineer}{Freelance}{Lima--Perú}{}
{
\begin{itemize}
    \item \textbf{Copa Master}
        \begin{itemize}
            \item Pioneered the complete project lifecycle from architecture to backend maintenance, emphasizing agile and adaptive development strategy.
            \item Embraced a TDD-centric approach ensuring quality control through comprehensive testing, which led to a seamless deployment process.
            \item Crafted and fine-tuned a continuous deployment pipeline, transitioning fluidly from CircleCI to AWS EKS, maximizing deployment efficiency and reliability.
        \end{itemize}
        \textbf{Tools:} Python, Django, PostgreSQL, JQuery, nose, Mock, Gunicorn, Supervisord, HTML5, CSS3, Git, Docker
\end{itemize}
}

\subsection{}

\cventry{2014}{Senior Python Software Engineer}{PASTPRESENTFUTURE}{Lima--Perú}{}
{
\url{https://pastpresentfuture.com}
\newline{}
\begin{itemize}
    \item \textbf{Doccupations}
        \newline{}
        WIP (\url{http://doccupations.com})
        \begin{itemize}
            \item Fostered an agile development culture by coaching clients and colleagues, enhancing team dynamics and project outcomes.
            \item Led the project inception, engineering a resilient and scalable backend architecture that resulted in an impressive 90\% code coverage through rigorous testing.
            \item Developed a robust continuous deployment pipeline with CircleCI, optimizing the software release lifecycle.
            \item Designed and implemented an asynchronous email delivery system using Celery with RabbitMQ, dramatically improving the efficiency and responsiveness of communication features.
            \item Enhanced text search capabilities through the integration of Apache Solr, delivering a superior user experience through quick and accurate search results.
        \end{itemize}
        \textbf{Tools:} Python, Django, Celery, RabbitMQ, PostgreSQL, Apache Solr, JQuery, nose, Mock, Gunicorn, Supervisord, Stripe, HTML5, CSS3, Git, CircleCI, Fabric
\end{itemize}
}

\subsection{}

\cventry{2013--2014}{Senior Python Software Engineer}{Bit Zeppelin}{Lima--Peru}{}
{
\begin{itemize}
    \item \textbf{An unnamed ERP system}
        \begin{itemize}
            \item Engaged in the intricate process of architecting and developing a sophisticated web-based interface for the previously desktop-only, open-source ERP system known as Tryton, necessitating the reverse engineering of the API due to the absence of any pre-existing technical documentation related to the client software interfaces.
            \item Implemented a comprehensive testing strategy, encompassing both unit tests and end-to-end tests, to ensure robust coverage and maintain the integrity and reliability of the codebase throughout the development lifecycle.
        \end{itemize}
        \textbf{Tools:} Python, Django, Tryton, MySQL, Scrapy, jQuery, HTML5, CSS3, Git, CircleCI, Fabric
    \item \textbf{A Mortgage Credit Web App}
        \begin{itemize}
            \item Assumed full responsibility for the backend maintenance of a critical mortgage credit web application, focusing on enhancing system performance and stability through meticulous code revisions and optimizations.
            \item Dedicated to maintaining high code quality, I rigorously applied unit testing methodologies to all modifications to ensure that each change adhered to the predefined standards and did not introduce any regressions or new bugs.
        \end{itemize}
        \textbf{Tools:} Python, Tornado, MongoDB, jQuery, HTML5, CSS3
    \item \textbf{UPC Job Board}
        \begin{itemize}
            \item Tasked with the ongoing maintenance of the backend systems for Scotiabank’s mobile banking platform, focusing on optimizing data handling and transaction processing to enhance user experience and system reliability.
            \item Committed to ensuring the stability and reliability of the platform, I employed unit testing on all new code implementations to validate functionality and prevent disruptions in service, adhering to strict quality assurance protocols.
        \end{itemize}
        \textbf{Tools:} Python, Django, PostgreSQL, Gunicorn, Supervisord, HTML5, CSS3
\end{itemize}
}

\subsection{}

\cventry{2012--2013}{Senior iOS \& Python Software Engineer}{Taller Technologies}{Lima--Peru}{}
{
\begin{itemize}
    \item \textbf{TList}
        \begin{itemize}
            \item As the software architect and principal engineer for the project, I spearheaded the development of the iOS frontend, meticulously crafting a robust architecture that seamlessly integrated with backend services, ensuring a fluid and responsive user experience while adhering to best practices in code quality and maintainability.
            \item The core functionalities I developed for the application included an advanced chat interface that allowed users to communicate through text and emojis, enhancing user engagement. Additionally, I implemented a dynamic user profile system where individuals could post statuses visible to their network, and a sophisticated search interface that enabled users to locate peers within their own and affiliated educational institutions, thereby fostering a connected community environment.
            \item During a period when Xcode lacked built-in continuous deployment capabilities, I took the initiative to construct a comprehensive CI pipeline from scratch. Utilizing Jenkins coupled with advanced bash scripting techniques, I established a robust deployment workflow that interfaced with the then-independent service TestFlight, prior to its acquisition by Apple, thus streamlining the development process and enhancing productivity.
        \end{itemize}
        \textbf{Tools:} Objective-C, AFNetworking, XMPPFramework, OCUnit, OCHamcrest, Frank, TestFlight
    \item \textbf{Context Aware Computing}
        \begin{itemize}
            \item As a pivotal contributor to the project, my role was primarily centered around leveraging my expertise in Python to architect and refine core functionalities, ensuring robust development practices while also facilitating knowledge transfer as a Python trainer to elevate the team's programming acumen.
            \item I was tasked with the development of mission-critical components, specifically utilizing Zope Interfaces to enhance modularity and reusability across the software architecture, thereby ensuring that the system's scalability and maintainability met the stringent requirements of our project's scope.
            \item My responsibilities also included conducting comprehensive training sessions focused on unit, integration, and end-to-end testing methodologies using advanced Python testing libraries, thereby significantly elevating the team's proficiency in delivering high-quality, bug-free code in alignment with industry best practices.
        \end{itemize}
        \textbf{Tools:} Python, Zope, Atlassian Bamboo
    \item \textbf{Staff Allocation Tool}
        \begin{itemize}
            \item As a Junior Software Engineer, I actively engaged in the project, leveraging my foundational knowledge in Java to contribute effectively to the development tasks, despite my initial status as a novice in the programming language, which provided a robust platform for my professional growth and skill enhancement.
            \item Employed Groovy extensively as an integral "glue" language to facilitate seamless continuous deployment processes, while utilizing Maven as a sophisticated dependency management tool to ensure consistent project builds and streamline the integration of various software components.
            \item Assumed a pivotal role in quality assurance by orchestrating the exploratory testing phase, meticulously examining and identifying potential discrepancies and areas for improvement within the software to uphold and enhance the product's reliability and user satisfaction.
        \end{itemize}
        \textbf{Tools:} Java, Spring, PrimeFaces, Maven, Groovy, Selenium, XML, Atlassian Bambo
\end{itemize}
}

\subsection{}

\cventry{2010--2012}{Senior iOS \& Python Software Engineer/Project Manager/Company Partner}{Bit Zeppelin}{Lima--Peru}{}
{
\begin{itemize}
    \item \textbf{Teleticket’s app}
        \begin{itemize}
            \item Implemented ASIHTTP library for asynchronous downloading on a secondary thread, enhancing application performance and user experience during intensive data transfers.
            \item Developed a feature using custom algorithms for autonomous downloading and synchronization of event data, ensuring up-to-date and accurate user interface, improving user engagement.
            \item Engineered mapping functionality with MapKit, placing pins for event venues on a digital map, providing intuitive geographical visualization, improving user navigation and planning in the app.
            \item Directed requirement gathering and transformed complex specifications into actionable user stories, streamlining development and aligning with stakeholder expectations and user needs.
            \item Oversaw a team of five developers, leading daily standups and scrum ceremonies, fostering a collaborative environment, accelerating timelines, and enhancing productivity through communication and feedback.
            \item Regularly communicated progress and updates to the client bi-weekly and post-sprint, ensuring transparency and maintaining strong relations by keeping them informed of milestones and strategic decisions.
        \end{itemize}
        \textbf{Tools:} Objective-C, Three20, ASIHTTP
    \item \textbf{tootalk}
        \begin{itemize}
            \item Developed and implemented the Speex codec in C for iOS and Android, enhancing audio compression and decompression for mobile communications.
            \item Led a rebranding of Linphone for tootalk, aligning its design and functionality with the corporate identity, enhancing user engagement and brand consistency.
            \item Focused on extracting and documenting software requirements, translating them into user stories for the sprint backlog, optimizing agile project management and development.
            \item As Software Architect and Project Manager, made key decisions on codec communication protocols and conducted load testing to ensure high audio quality and performance.
            \item Managed and mentored four Junior Developers in integrating corporate branding into the application, ensuring alignment with brand strategy and corporate identity standards.
        \end{itemize}
        \textbf{Tools:} Objective-C, Three20, Linphone, C
    \item \textbf{mitiempo.pe}
        \begin{itemize}
            \item Undertook my first iOS project, learning Objective-C and Cocoa Touch quickly. After a month of intensive training, I started developing complex iOS apps using Apple's frameworks.
            \item Initially used a cascading-style project management due to limited agile knowledge. This approach led to speculative project estimations without iterative feedback or improvements.
            \item The app's testing was done manually, involving detailed simulation of user interactions to find bugs and evaluate usability, without using automated testing frameworks.
            \item Outsourced backend development required strict coordination and communication to integrate third-party services smoothly with front-end operations, ensuring compliance with project specifications and timelines.
        \end{itemize}
        \textbf{Tools:} Objective-C, Facebook’s Three20
\end{itemize}
}

\subsection{}

\cventry{2010}{Senior Python \& C\# Software Engineer}{ICTEC}{Lima--Peru}{}
{
\begin{itemize}
    \item \textbf{Neoauto}
        \begin{itemize}
            \item Engaged in a comprehensive maintenance session aimed at enhancing the system's operational efficiency, with a specific focus on integrating the advanced advertising module. This integration not only optimizes ad placement algorithms but also leverages cutting-edge targeting techniques to improve user engagement and revenue generation capabilities.
        \end{itemize}
        \textbf{Tools:}  Python, Django, MySQL, jQuery, HTML, CSS, Subversion
    \item \textbf{VHF Radio Device Driver for Orion}
        \begin{itemize}
            \item Leveraging the foundational capabilities of an existing software interface that facilitated communication with the radio system, I engineered an advanced proof-of-concept for the Orion's driver utilizing Python. This prototype incorporated the strategic replication of the payload from the aforementioned software, thereby enabling seamless interoperability between diverse radio systems through the Python-based mock-up, thus demonstrating the potential for scalable integration in communication technologies.
            \item Transitioning from the prototype phase to production, I meticulously developed the definitive version of the Orion's driver using C\#, focusing on robustness and efficiency. This development process, not only involved coding but also meticulous integration and packaging of the driver into the final product, ensuring that the software met all operational requirements and was ready for deployment in complex environments, thereby enhancing the communication infrastructure.
            \item In a critical demonstration to the Quality Assurance Committee of the Peruvian Army, I presented the fully developed Orion's driver, articulating its features, operational benefits, and compliance with stringent military standards. This presentation, detailed and comprehensive, culminated in obtaining the final approval from the committee, affirming the driver’s readiness for field deployment and its alignment with the strategic communication objectives of the military.
        \end{itemize}
        \textbf{Tools:} IronPython, .NET
\end{itemize}
}

\subsection{}

\cventry{2006--2009}{Mid-Senior Python Software Engineer}{Aureal}{Lima--Peru}{}
{
\begin{itemize}
    \item \textbf{Neoauto}
        \begin{itemize}
            \item As the technical lead for the project, I spearheaded the development process, overseeing a team of skilled engineers and ensuring that all technical aspects aligned with the strategic objectives, thereby facilitating a streamlined and efficient project execution.
            \item Despite the frontend components being developed externally by a specialized Uruguayan firm, our team undertook a significant refactoring of the HTML and CSS codebases to ensure seamless integration and optimal performance within the Django framework, enhancing both maintainability and scalability of the web applications.
            \item I actively engaged in and promoted Extreme Programming (XP) methodologies, specifically Test-Driven Development (TDD) and pair programming, to foster a collaborative environment and enhance code quality, which significantly contributed to reducing bugs and accelerating the development cycle.
            \item I was responsible for compiling an exhaustive set of technical documentation using Sphinx, which included detailed Python docstrings that served as a crucial reference tool for both current and future development phases, ensuring consistency and comprehension across the technical team.
            \item Simultaneously developed the platforms Aptitus and Neoauto, which necessitated the creation of robust core libraries that were utilized across both projects to streamline development processes, reduce redundancy, and maintain a high standard of code efficiency and reusability.
        \end{itemize}
        \textbf{Tools:} Python 2.5, Django 1.x, OpenID, Memcached, South, MySQL, CSS, HTML, Vanilla Javascript, Subversio
    \item \textbf{Aptitus}
        \begin{itemize}
            \item As the technical lead for the project, I spearheaded the development team, strategically guiding the architectural decisions and ensuring the integration of cutting-edge technologies to meet the project's objectives, while also fostering an environment conducive to innovative problem-solving and high-quality software development.
            \item I actively engaged in the implementation of Extreme Programming (XP) practices, specifically focusing on Test-Driven Development (TDD) and Pair Programming, to enhance code quality and reliability through rigorous testing protocols and collaborative coding sessions, thereby significantly reducing bug rates and accelerating the feature development process.
            \item I was responsible for compiling all the technical documentation using Sphinx, meticulously documenting Python docstrings to create a comprehensive and navigable documentation repository that supports both current project needs and future maintenance efforts by providing clear, detailed explanations of code functionalities and APIs.
            \item Simultaneously developed the platforms Aptitus and Neoauto, which necessitated the creation of robust core libraries that were utilized across both projects to streamline development processes, reduce redundancy, and maintain a high standard of code efficiency and reusability.
        \end{itemize}
        \textbf{Tools:} Python 2.5, Django 1.x, OpenID, Memcached, South, MySQL, CSS, HTML, Vanilla Javascript, Subversion
    \item \textbf{Americatel's ERP}
        \begin{itemize}
            \item Actively engaged in the systematic maintenance and enhancement of software functionalities, focusing on the integration and deployment of new features designed to optimize system performance and user interaction, ensuring alignment with the project's strategic objectives and operational requirements.
            \item Employed a sophisticated cascading-style project management approach, wherein comprehensive testing phases were strategically scheduled to follow the completion of all developmental updates, thereby facilitating a streamlined and efficient validation process to maintain the highest standards of software integrity and reliability.
        \end{itemize}
        \textbf{Tools:} Python 2.4, Django 0.95, MySQL, CSS, HTML, Vanilla Javascript, Subversion
\end{itemize}
}

\subsection{}

\section{Education}
\cventry{1999--2002}
    {Undergraduate degree}
    {Instituto Superior Tecnológico de Ciencias de la Información}{Lima--Perú}
    {}{Ex-Instituto de Ciencias de la Información de la Universidad Nacional de Ingeniería}

\subsection{}

\cventry{1996--1998}
    {Diploma}
    {Colegio de la Inmaculada}{Lima--Perú}
    {}{}

\subsection{}

\section{References}
\cvlistitem
{
    \textbf{Robert Werner}
    \newline{}
    Senior Software Engineer at Goodyear Tire \& Rubber
    \newline{}
    \url{https://www.linkedin.com/in/robertmdwerner}
}
\cvlistitem
{
    \textbf{Sandra Quiroz}
    \newline{}
    Head of Development at Encora Lima
    \newline{}
    \url{https://www.linkedin.com/in/sandradiazquiroz}
}
\cvlistitem
{
    \textbf{Breno Colom}
    \newline{}
    Software Engineer at Scrapinghub
    \newline{}
    \url{https://linkedin.com/in/brenocolom}
}
\end{document}
