%% start of file `Jean-Pierre.Chauvel.Résumé.tex`
%% Copyright 2016 Jean-Pierre Chauvel <jean.pierre@chauvel.org>

\documentclass[11pt,a4paper,english]{moderncv}
% moderncv theme
\moderncvtheme[grey]{casual}
% document language
\usepackage[english]{babel}
% character encoding
\usepackage[utf8]{inputenc}
% adjust page margins
\usepackage[scale=0.8]{geometry}
% in preamble:
\SetExpansion[stretch = 70, shrink = 70,] { encoding = {T2A} } { }
\DeclareMicrotypeSet{t2atext}{encoding=T2A}
\UseMicrotypeSet{t2atext}

%personal data
\name{Jean-Pierre}{Chauvel}
\address{Lima, Perú}{}
%\email{jean.pierre@chauvel.org}
\email{jean.pierre@chauvel.org}
\homepage{www.chauvel.org}
%\social[twitter]{hellhoundorf}
\social[whatsapp]{+51989804478}
\social[linkedin]{jpchauvel}
\social[github]{jpchauvel}
\quote{Boasting nearly two decades of crafting enterprise solutions, I stand as a champion of agile methodologies with a robust Python backend expertise. My affinity for Vim epitomizes my fusion of classic rigor with contemporary agility.}

\begin{document}
\maketitle

\section{Recent Experience}

\cventry{2017--Present}{Senior Python Software Engineer}{Encora}{Lima--Peru}{}
{
\url{https://encora.com}
\newline{}
\begin{itemize}
    \item \textbf{Goodyear's AndGo}
        \newline{}
        \url{https://www.andgonow.com}
        \begin{itemize}
            \item Spearheaded the creation of comprehensive technical specifications and diagrams to crystallize product requirements, facilitating seamless communication between developers and stakeholders.
            \item Implemented Test-Driven Development (TDD) diligently, maintaining code coverage above 90\% for unit, integration, and end-to-end tests, ensuring robust and reliable software deliveries.
            \item Played a pivotal role in decomposing a monolithic service into a suite of focused microservices, taking utmost care in rearchitecting database schema for scalability and resilience.
            \item Led the development of a critical feature for the automation of calendar events, enhancing process efficiency through meticulous forward-planning.
        \end{itemize}
        \textbf{Tools:} Python, asyncio, Flask, SQLAlchemy, PostgreSQL, Mock, Git, Docker, Microservices
    \item \textbf{Tribal Planet's MPACT}
        \newline{}
        \url{https://www.tribalplanet.com}
        \begin{itemize}
            \item Orchestrated the architectural blueprint and championed backend development, maintaining cutting-edge application infrastructure.
            \item Elevated test coverage with a TDD approach for a watertight, bug-resistant production environment.
            \item Innovated a robust continuous deployment pipeline using CircleCI and AWS EKS to streamline software delivery. 
            \item Augmented performance by offloading computationally intensive tasks to Celery jobs, optimizing asynchronous operations.
            \item Engineered an automated content moderation system using AWS Rekognition and Azure Cognitive Services that upheld content quality and compliance.
        \end{itemize}
        \textbf{Tools:} Python, asyncio, Flask, SQLAlchemy, MySQL, MongoDB, Mock, Git, Docker
    \item \textbf{Scotiabank's mobile banking}
        \begin{itemize}
            \item Contributed to the development of the iOS app using Objective-C, ensuring adherence to industry best practices and a consistent user experience.
            \item Upheld TDD principles to guarantee comprehensive unit test coverage, fostering reliability in app releases.
            \item Utilized the GitFlow branching model to maintain a stable and methodical software versioning rhythm.
        \end{itemize}
        \textbf{Tools:} Objective-C, Swift 4.1, Carthage, Git
\end{itemize}
}

\subsection{}

\cventry{2016}{Senior Python Software Engineer}{Freelance}{Lima--Perú}{}
{
\begin{itemize}
    \item \textbf{Copa Master}
        \begin{itemize}
            \item Pioneered the complete project lifecycle from architecture to backend maintenance, emphasizing agile and adaptive development strategy.
            \item Embraced a TDD-centric approach ensuring quality control through comprehensive testing, which led to a seamless deployment process.
            \item Crafted and fine-tuned a continuous deployment pipeline, transitioning fluidly from CircleCI to AWS EKS, maximizing deployment efficiency and reliability.
        \end{itemize}
        \textbf{Tools:} Python, Django, PostgreSQL, JQuery, nose, Mock, Gunicorn, Supervisord, HTML5, CSS3, Git, Docker
\end{itemize}
}

\subsection{}

\cventry{2014}{Senior Python Software Engineer}{PASTPRESENTFUTURE}{Lima--Perú}{}
{
\url{https://pastpresentfuture.com}
\newline{}
\begin{itemize}
    \item \textbf{Doccupations}
        \newline{}
        WIP (\url{http://doccupations.com})
        \begin{itemize}
            \item Fostered an agile development culture by coaching clients and colleagues, enhancing team dynamics and project outcomes.
            \item Led the project inception, engineering a resilient and scalable backend architecture that resulted in an impressive 90\% code coverage through rigorous testing.
            \item Developed a robust continuous deployment pipeline with CircleCI, optimizing the software release lifecycle.
            \item Designed and implemented an asynchronous email delivery system using Celery with RabbitMQ, dramatically improving the efficiency and responsiveness of communication features.
            \item Enhanced text search capabilities through the integration of Apache Solr, delivering a superior user experience through quick and accurate search results.
        \end{itemize}
        \textbf{Tools:} Python, Django, Celery, RabbitMQ, PostgreSQL, Apache Solr, JQuery, nose, Mock, Gunicorn, Supervisord, Stripe, HTML5, CSS3, Git, CircleCI, Fabric
\end{itemize}
}

\subsection{}

\section{Education}
\cventry{1999--2002}
    {Undergraduate degree}
    {Instituto Superior Tecnológico de Ciencias de la Información}{Lima--Perú}
    {}{Ex-Instituto de Ciencias de la Información de la Universidad Nacional de Ingeniería}

\subsection{}

\cventry{1996--1998}
    {Diploma}
    {Colegio de la Inmaculada}{Lima--Perú}
    {}{}

\subsection{}

\section{References}
\cvlistitem
{
    \textbf{Robert Werner}
    \newline{}
    Senior Software Engineer at Goodyear Tire \& Rubber
    \newline{}
    \url{https://www.linkedin.com/in/robertmdwerner}
}
\cvlistitem
{
    \textbf{Sandra Quiroz}
    \newline{}
    Head of Development at Encora Lima
    \newline{}
    \url{https://www.linkedin.com/in/sandradiazquiroz}
}
\cvlistitem
{
    \textbf{Breno Colom}
    \newline{}
    Software Engineer at Scrapinghub
    \newline{}
    \url{https://linkedin.com/in/brenocolom}
}
\end{document}
