%% start of file `Jean-Pierre.Chauvel.Résumé.tex`
%% Copyright 2016 Jean-Pierre Chauvel <jchauvel@gmail.com>

\documentclass[11pt,a4paper,english]{moderncv}
% moderncv theme
\moderncvtheme[grey]{casual}
% document language
\usepackage[english]{babel}
% character encoding
\usepackage[utf8]{inputenc}
% adjust page margins
\usepackage[scale=0.8]{geometry}
% in preamble:
\SetExpansion[stretch = 70, shrink = 70,] { encoding = {T2A} } { }
\DeclareMicrotypeSet{t2atext}{encoding=T2A}
\UseMicrotypeSet{t2atext}

%personal data
\firstname{Jean-Pierre Chauvel}
\familyname{}
\address{Lima, Perú}{}
%\email{jchauvel@gmail.com}
\email{jean.pierre@chauvel.org}
%\social[twitter]{hellhovnd}
\social[linkedin]{helhound}
\social[github]{jpchauvel}
\quote{I have almost 20 years of experience developing enterprise solutions. I’m an agile thinker with strong Python development background. Also, I am a technical Python backend evaluator. My editor of choice is Vim but that doesn’t mean I wear an old-school programmer’s hat!}

\begin{document}
\maketitle

\section{Experience}

\cventry{2017--present}{Senior Python Software Engineer}{Encora}{Lima--Peru}{}
{
\url{https://encora.com}
\newline{}
\begin{itemize}
    \item \textbf{Scotiabank's mobile banking}
        \newline{}
	    Worked on developing the iOS app.
        \newline{}
        \textbf{Tools:} Objective-C, Swift 4.1, Carthage, Git
    \item \textbf{Tribal Planet's Citizen Earth}
        \newline{}
        Gave maintenance to the RESTful backend. Citizen Earth is a mobile based engagement app that encourages users to participate in activities related to sustainability and clean energy generation.
        \newline{}
        \textbf{Tools:} Python, asyncio, Flask, SQLAlchemy, MySQL, MongoDB, Mock, Git
    \item \textbf{Goodyear's AndGo}
        \newline{}
        \url{https://www.andgonow.com}
        \newline{}
        A predictive vehicle servicing platform that offers full vehicle readiness, keeping cars safer, serviced and ready to go wherever they’re needed.
        \newline{}
        \textbf{Tools:} Python, asyncio, Flask, SQLAlchemy, PostgreSQL, Mock, Git
\end{itemize}
}

\subsection{}

\cventry{2017}{iOS Software Engineer}{Dipoo SAC}{Telecommute, Lima--Peru}{}
{
\begin{itemize}
    \item \textbf{Bederr}
        \newline{}
        Bederr is an iOS/Android app that aggregates venues and benefits from the current location of the user. My job consisted in giving it a new face to the UI and give it maintainance to the business logic.
        \newline{}
        \textbf{Tools:} Objective-C (iOS), OCMockito, Core Location, Google Maps, Circle CI, HockeyApp, CocoaPods
\end{itemize}
}

\subsection{}

\cventry{2016--2017}{iOS Software Engineer}{Freelance}{Lima--Perú}{}
{
\begin{itemize}
    \item \textbf{Aldo Mariátegui's Ensayos Impopulares}
        \newline{}
        An iOS-WordPress client. I had to build a WordPress adapter in Python to built a REST API using JSON Documents to ease the development of the iOS app.
        \newline{}
        \textbf{Tools:} Objective-C (iOS), AFNetworking, OCUnit (SenTestingKit), OCHamcrest, Python, Django, Django RESTFramework, nose, Mock, Gunicorn, Supervisord, XML, Travis-CI, Fabric
\end{itemize}
}

\subsection{}

\cventry{2016}{Senior Python Software Engineer}{Freelance}{Lima--Perú}{}
{
\begin{itemize}
    \item \textbf{Copa Master}
        \newline{}
        A campaign website for the newspaper "El Bocón", which is a product of EPENSA (a local newspaper company). It allowed users to build soccer teams and vote for their favorite team. When the campaing reached its deadline users could not vote for any team and 8 teams would be selected to play a tournament.
        \newline{}
        \textbf{Tools:} Python, Django, PostgreSQL, JQuery, nose, Mock, Gunicorn, Supervisord, HTML5, CSS3, Git, Docker
\end{itemize}
}

\subsection{}

\cventry{2014}{Senior Python Software Engineer}{PASTPRESENTFUTURE}{Lima--Perú}{}
{
\url{https://pastpresentfuture.com}
\newline{}
\begin{itemize}
    \item \textbf{Doccupations}
        \newline{}
        WIP (\url{http://doccupations.com})
        \newline{}
        A Django-based job-exchange website for Dentists. I've used Celery and RabbitMQ to coordinate asynchronous emails and full-text searches. Haystack and Apache Solr were used to handle the full-text job searches and job automatches.
        \newline{}
        \textbf{Tools:} Python, Django, Celery, RabbitMQ, PostgreSQL, Apache Solr, JQuery, nose, Mock, Gunicorn, Supervisord, Stripe, HTML5, CSS3, Git, CircleCI, Fabric
\end{itemize}
}

\subsection{}

\cventry{2013--2014}{Senior Python Software Engineer}{Bit Zeppelin}{Lima--Perú}{}
{
\url{https://bitzeppelin.com}
\newline{}
\begin{itemize}
    \item \textbf{Enterprise Resource Planning System (ERP)}
        \newline{}
	    Worked on developing the core of a web based wrapper/interface for a desktop ERP based on Tryton. Web crawling/spider development of several websites to feed as data for the demo version of the ERP.
        \newline{}
        \textbf{Tools:} Python, Django, Tryton, Scrapy, JQuery, nose, Mock, Gunicorn, Supervisord, HTML5, CSS3, Git, CircleCI, Fabric
    \item \textbf{Crédito Hipotecario}
        \newline{}
        Tornado and MongoDB CMS for a real state product of a peruvian bank.
        \newline{}
        \textbf{Tools:} Python, Tornado, MongoDB, JQuery, nose, Mock, HTML5, CSS3, Git
    \item \textbf{UPC Job Board}
        \newline{}
        Django/PostgreSQL job board web app for Universidad Peruana de Ciencias Aplicadas, a leading university in Peru.
        \newline{}
        \textbf{Tools:} Python, Django, PostgreSQL, Apache Solr, JQuery, nose, Mock, Gunicorn, Supervisord, HTML5, CSS3, Git
\end{itemize}
}

\subsection{}

\cventry{2012--2013}{Senior iOS \& Python Software Engineer}{Taller Technologies}{Lima--Perú}{}
{
\url{https://tallertechnologies.com}
\newline{}
\begin{itemize}
    \item \textbf{Staff Allocation Tool}
        \newline{}
        A Spring/Java, web-app, pet-project made for resource management.
        \newline{}
        \textbf{Tools:} Java, Spring, PrimeFaces, Maven, Selenium, XML, Git, Atlassian Bamboo
    \item \textbf{Context Aware Computing}
        \newline{}
        An ongoing cloud-computing project on Intel. I spent my time mostly as a Pythonista specialist for the dev team.
        \newline{}
        \textbf{Tools:} Python, Mock, Git, Atlassian Bamboo
    \item \textbf{Kohl's Campus Kiosk}
        \newline{}
        Kohl's solution for internship application on-site. I was in charge of the iPad frontend.
        \newline{}
        \textbf{Tools:} Objective-C (iOS), Core Data, AFNetworking, OCUnit (SenTestingKit), OCHamcrest, Git, TestFlight
    \item \textbf{TList (now known as Chatpass.me)}
        \newline{}
        An end-user, social-networking iOS app focused on the tween and teen market sectors. Its features are somewhat similar to the LINE and Whatsapp apps. I was the main software architect and the lead Engineer of the frontend.
        \newline{}
        \textbf{Tools:} Objective-C (iOS), AFNetowking, XMPPFramework, OCUnit (SenTestingKit), OCHamcrest, Frank, Git, TestFlight
\end{itemize}
}

\subsection{}

\cventry{2010--2012}{Senior iOS \& Python Software Engineer/Project Manager/Company Partner}{Bit Zeppelin}{Lima--Perú}{}
{
\url{https://bitzeppelin.com}
\newline{}
\begin{itemize}
    \item \textbf{Interbank's mitiempo.pe}
        \newline{}
        Published \url{http://j.mp/mitiempo_pe}
        \newline{}
        \textbf{Tools:} Objective-C (iOS), Three20, OCUnit (SenTestingKit), Git
    \item \textbf{Global Backbone's tootalk}
        \newline{}
        Published \url{http://j.mp/tootalk}
        \newline{}
        \textbf{Tools:} Objective-C (iOS), Three20, Linphone, OCUnit (SenTestingKit), Git
    \item \textbf{E.Wong's Shopping list}
        \newline{}
        Not published
        \newline{}
        \textbf{Tools:} Objective-C (iOS), Three20, OCUnit (SenTestingKit), Git
    \item \textbf{Teleticket's app}
        \newline{}
        Published \url{http://j.mp/teleticket-ios}
        \newline{}
        \textbf{Tools:} Objective-C (iOS), Three20, ASIHTTP, OCUnit (SenTestingKit), Git
    \item \textbf{Plaza Vea's app}
        \newline{}
        \textbf{Tools:} Objective-C (iOS), Core Data, OCUnit (SenTestingKit), Git
\end{itemize}
}

\subsection{}

\cventry{2010}{Senior Python \& C++ Software Engineer}{ICTEC}{Lima--Perú}{}
{
\url{https://itctec.biz}
\newline{}
\begin{itemize}
    \item \textbf{Software for military-grade equipment}
        \newline{}
        Orion is a Tactical Command and Control System used by the Peruvian Army. The driver I've developed allowed the system to be used with the Israeli Tadiran CNR 9000 radio equipment to send tactical maps and flash messages between VHF stations.
        \newline{}
        \textbf{Tools:} C++, C\#, Subversion
    \item \textbf{NeoAuto's resale submodule}
        \newline{}
        \url{http://neoauto.pe}
        \newline{}
        \textbf{Tools:} Python, Django, MySQL, JQuery, HTML, CSS2.1, Subversion
\end{itemize}
}

\subsection{}

\cventry{2009}{Senior Python Software Engineer}{Grupo El Comercio}{Lima--Perú}{}
{
\url{https://grupoelcomercio.com.pe}
\newline{}
\begin{itemize}
    \item \textbf{Aptitus' backend maintenance}
        \newline{}
        \url{http://aptitus.pe}
        \newline{}
        \textbf{Tools:} Python, Django, MySQL, JQuery, HTML, CSS2.1, Subversion
    \item \textbf{Neoauto's backend maintenance}
        \newline{}
        \url{http://neoauto.pe}
        \newline{}
        \textbf{Tools:} Python, Django, MySQL, JQuery, HTML, CSS2.1, Subversion
\end{itemize}
}

\subsection{}

\cventry{2006--2009}{Mid-Senior Python Software Engineer}{Aureal}{Lima--Perú}{}
{
\url{https://aureal.pe}
\newline{}
\begin{itemize}
    \item \textbf{Aptitus: a labor exchange website for Grupo El Comercio}
        \newline{}
        \url{http://aptitus.pe}
        \newline{}
        \textbf{Tools:} Python, Django, MySQL, JQuery, HTML, CSS2.1, Subversion
    \item \textbf{Neoauto: a car-sale website for Grupo El Comercio}
        \newline{}
        \url{http://neoauto.pe}
    \item \textbf{Relax: adult-oriented website for Grupo El Comercio}
        \newline{}
        Never published
        \newline{}
        \textbf{Tools:} Python, Django, MySQL, JQuery, HTML, CSS2.1, Subversion
    \item \textbf{Tumax: a social-network site for Grupo El Comercio}
        \newline{}
        Never published
        \newline{}
        \textbf{Tools:} Python, Django, MySQL, JQuery, HTML, CSS2.1, Subversion
    \item Finance and Accounting System for Americatel
\end{itemize}
}

\subsection{}

\cventry{2004--2006}{C++ COM Component Software Engineer}{Applisys}{Lima--Perú}{}
{
\url{https://applisys.com.pe}
\newline{}
Main work was focused on developing COM components for their APPLISIG ERP
}

\subsection{}

\cventry{2003-2004}{PHP Software Engineer}{OyM System Group}{Asunción--Paraguay}{}
{
\url{https://oym.com.py}
\newline{}
Migration of their enterprise application framework from FoxPro for DOS to Visual FoxPro 9
}

\subsection{}

\cventry{2002}{Junior Software Engineer}{Tecniaduanas}{Lima--Perú}{}
{
\url{https://tli.com.pe}
\newline{}
Bug fixing and maintainance to their in-house-developed ERP
}

\subsection{}

\section{Education}
\cventry{1999--2002}
    {Undergraduate degree}
    {Instituto Superior Tecnológico de Ciencias de la Información}{Lima--Perú}
    {}{Ex-Instituto de Ciencias de la Información de la Universidad Nacional de Ingeniería}

\subsection{}

\cventry{1996--1998}
    {Diploma}
    {Colegio de la Inmaculada}{Lima--Perú}
    {}{}

\clearpage
    

\section{References}
\cvlistitem
{
    \textbf{Robert Werner}
    \newline{}
    Senior Software Engineer at Goodyear Tire \& Rubber
    \newline{}
    \url{https://www.linkedin.com/in/robertmdwerner}
}
\cvlistitem
{
    \textbf{Sandra Quiroz}
    \newline{}
    Head of Development at Encora Lima
    \newline{}
    \url{https://www.linkedin.com/in/sandradiazquiroz}
}
\cvlistitem
{
    \textbf{Ron Buell}
    \newline{}
    CTO at Tribal Planet
    \newline{}
    \url{https://www.linkedin.com/in/ron-buell-28a2344/}
}
\cvlistitem
{
    \textbf{Breno Colom}
    \newline{}
    Software Engineer at Scrapinghub
    \newline{}
    \url{https://linkedin.com/in/brenocolom}
}
\end{document}
